Full Brain Blood-Oxygen-Level-Dependent Signal \\ Parameter Estimation using Sequential Monte Carlo Methods

### 2010-08-25 doc/presentation/main.tex
added a frame where the graphs of the timeseries will go
got multihead working and added a script to start the show
new additions in nonlinear

\documentclass{beamer}
%\usepackage[orientation=landscape,size=custom,width=16,height=10,scale=0.5]{beamerposter} 
%\setbeameroption{show notes on second screen}

@@

\section{Introduction}
\begin{frame}{Balloon Model}
\begin{figure}
\includegraphics[width=10cm]{model}
\caption{
    \tiny
    \cite{nonlinearfiltering}
}
\end{figure}
\note{Rates range from below 1 Hz to 5 to 6 Hundred Hz}
\note{Change in average firing rates increase metabolism and sympathetic response causes
        increased inflow of oxygenated blood.}
\note{In the version of the Balloon model I used, the flow is locked to metabolism.}
\note{According the balloon model this increases the local blood volume, and the outflow pressure.}
\note{So the signal is altered by changes in the ratio of Deoxyhemoglobin and Oxygenated Hemoglobin,
        which are a function of Volume and Oxygenation.}
\end{frame}

@@

\begin{frame}{Solutions: Approximate Method}
  \begin{itemize}
    \item 2nd Order Volterra Kernel 
    \note{Quadratic Approximation}
    \begin{itemize}
        \item Quadratic Convolution used to approximate Jacobian Matrix.
        \note{Because of the nonlinearities in the BOLD model, step size for
                integrating would otherwise be extremely small}
        \item Volterra approximation quality is not known.
    \end{itemize}
    \note{Volterra Approximation depends on sparsity etc}
    {\footnotesize
    $$y(t) = k_0 + \int_{-\infty}^{\infty} k_1(s_1) x(t-s_1) ds_1
        + \int_{-\infty}^{\infty} k_2(s_1,s_2) x(t-s_1)x(t-s_2) ds_1 ds_2$$
        \note{Its possible this isn't even knowable}
    }
    \item Canonical Hemodynamic Response Function
    \note{Linear Approximation}
    \begin{itemize}
        \item No Parameters Estimated
        \item Maximum Likelihood Possible
        \item Inflexible - even to changes in onset time
    \end{itemize}
    \begin{center}
    \includegraphics[clip=true,trim=4.88cm 0cm 5cm 1.5cm,height=2.7cm,width=8cm]{HRF}
    \end{center}

  \end{itemize}
\end{frame}

@@

%\begin{frame}{Model Comparison}
%    \includegraphics[width=5in,height=2.4in]{comparison.png}
%        \cite{comparison}

@@

\begin{frame}[allowframebreaks]
  \bibliographystyle{abbrvnat}
  \bibliography{references}
\end{frame}

>>>>

\documentclass{beamer}
%\usepackage[orientation=landscape,size=custom,width=16,height=10,scale=0.5]{beamerposter}

%\usepackage{pgfpages}
%\setbeameroption{show notes on second screen}

@@

\section{Introduction}
\begin{frame}{Balloon Model}
\begin{figure}
\includegraphics[width=10cm]{model}
\caption{
    \tiny
    \cite{Riera2003}
}
\end{figure}
\note{Rates range from below 1 Hz to 5 to 6 Hundred Hz}
\note{Change in average firing rates increase metabolism and sympathetic response causes
        increased inflow of oxygenated blood.}
\note{In the version of the Balloon model I used, the flow is locked to metabolism.}
\note{According the balloon model this increases the local blood volume, and the outflow pressure.}
\note{So the signal is altered by changes in the ratio of Deoxyhemoglobin and Oxygenated Hemoglobin,
        which are a function of Volume and Oxygenation.}
\end{frame}

\begin{frame}{Time Changing Parameters}
    \note{Should include a picture of the different parts of the BOLD signal}
\end{frame}

@@

\section{Regression}
\begin{frame}{Approximate Method}
  \begin{itemize}
    \item 2nd Order Volterra Kernel \cite{Friston2000}
    \note{Quadratic Approximation}
    \begin{itemize}
        \item Quadratic Convolution used to approximate Jacobian Matrix.
        \note{Because of the nonlinearities in the BOLD model, step size for
                integrating would otherwise be extremely small}
        \item Volterra approximation quality is not known.
    \end{itemize}
    \note{Volterra Approximation depends on sparsity etc}
    {\footnotesize
    $$y(t) = k_0 + \int_{-\infty}^{\infty} k_1(s_1) x(t-s_1) ds_1
        + \int_{-\infty}^{\infty} k_2(s_1,s_2) x(t-s_1)x(t-s_2) ds_1 ds_2$$
        \note{Its possible this isn't even knowable}
    }
    \item Canonical Hemodynamic Response Function
    \note{Linear Approximation}
    \begin{itemize}
        \item No Parameters Estimated
        \item Maximum Likelihood Possible
        \item Inflexible - even to changes in onset time
    \end{itemize}
    \begin{center}
    \includegraphics[clip=true,trim=4.88cm 0cm 5cm 1.5cm,height=2.7cm,width=8cm]{HRF}
    \end{center}

  \end{itemize}
\end{frame}

\begin{frame}{Nonlinear Modeling}
\begin{itemize}
    \item Local Linearization filter \cite{Riera2003}
     \note{Jacobian of the $\dot{x}$ is available, making gradient descent possible}
    \item Genetic Algorithms and Simulated Annealing \cite{Vakorin2007}
     \note{Genetic Algorithms were used to optimize spike points, simulated annealing for the parameters}
    \item Particle Filters to estimate $P(X_t | \Theta, Y_T)$ \cite{Murray2009}
    \begin{itemize}
        \item ML estimate of $\Theta$ based on $P(X_t | \Theta, Y_t)$ \cite{Johnston2007}
         \note{Particle Filter used to estimate states, ML of parameters based on the posterior of states and so on}
    \end{itemize}
    \item Unscented Kalman Filter to estimate parameters \cite{Hu2009}
    \item Direct Particle Filter, used in this work
     \note{Technically Kalman Filters and Particle Filters are Bayesian Filters}
     \note{Essentially filtering out inconsistent parameters.}
\end{itemize}
\end{frame}

@@

@@

\begin{frame}[allowframebreaks]
  \bibliographystyle{plain}
  \bibliography{../library}
\end{frame}
